---
output:
  word_document: default
  html_document: default
---
VL Relapse analysis 15 Dev 2021

PRE-PROCESSING THE FINAL DATASET FOR ANALYSIS:

I)Creating drug classes, follow up duration related variables.
II) Adding residuals to 0 event studies
III) Filtering out studies:
  1. Removing HIV co-infection based studies
  2. Missing info
  3. < 6month follow-up
  4. Unpublished (already removed)

```{r message=FALSE, warning=FALSE, include=FALSE}

library(readr)
library(readxl)
# meta-analysis packages
library(meta)
library(metafor )
#library(metagen)
library(metasens) 
# graphics packages
library(tidyverse)
library(reshape)
library(doBy)
library(stringr)
library(ggpubr)
library(patchwork)
library(dplyr)
library(data.table)

setwd("~/IDDO/Data")

#Pre-processed data (see Prepoc.R for the steps)
#Pick up latest cleaned file
#Check OneNote for the latest version

vl_main <- read_csv("vldata_clean_1129.csv") 
length(unique(vl_main$pub_id))

#Additional variables from the study design: Relapse definitions, servere cases inclusion, tyoe if VL cases.

relapse_def <- read_excel("vl_studydesign.xlsx", 
    sheet = "outcome_defintion", col_types = c("numeric", 
        "skip", "skip", "text", "text"))

relapse_def$relapse_method<-tolower(relapse_def$relapse_method)

vl_sev <- read_excel("vl_studydesign.xlsx", 
    sheet = "disease_severity", col_types = c("skip", 
        "numeric", "skip", "numeric", "skip", 
        "text", "numeric", "skip", "text", 
        "skip", "text"))
#Dont change order in the raw excel file


setDT(vl_sev)[, arm_no := rowid(tag)]
vl_sev$id<-paste0(vl_sev$tag,"_",vl_sev$arm_no)
vl_sev$tag<-NULL
vl_sev$Arm_ID<-NULL
vl_sev$arm_no <-NULL

vl_sae <- read_excel("VL_SAE.xlsx", sheet = "VL_SAEs_per_arm_04_12_2019", 
col_types = c("skip", "skip", "skip", 
   "numeric", "skip", "numeric", "skip", 
       "skip", "skip", "skip", "skip", "text", 
       "skip", "skip", "numeric", "numeric", 
        "skip", "skip", "skip", "skip", "skip"))

vl_sae$id<-paste0(vl_sae$Tag,"_",vl_sae$Repeat.Instance )
vl_sae$Tag<-NULL
vl_sae$Repeat.Instance<-NULL

vl_6monthplus_relapse <- read_excel("vl_6monthplus_relapse.xlsx")
vl_6monthplus_relapse$id<-paste0(vl_6monthplus_relapse$pub_id,"_",vl_6monthplus_relapse$redcap_repeat_instance)
vl_6monthplus_relapse$pub_id<-NULL
vl_6monthplus_relapse$redcap_repeat_instance<-NULL

df<-vl_main[,c('pub_id',
               'st_intv_arms',
               'redcap_repeat_instance',
               'st_followup',
              'me_hiv_yn',
               'eff_arm_icure_num',
               'eff_arm_icure_days',
               'eff_arm_relapse_num',
               'eff_arm_relapse_days',
               'st_status',
               'st_design',
               'st_allocation',
               'st_country_num',	
               'st_country1',
               'st_region',
               'sa_num_tx'	,
               'sa_num_followup',
               'sa_combi',
               'sa_intv1_drug',
               'sa_intv1_dose_mgkg',
               'sa_intv1_freq_discrete',
              'sa_intv1_freq_new',
              'sa_int1_total_dose',
               'sa_intv1_dura',
               'sa_intv1_reg_detail' ,
               'sa_intv2_drug',
               'sa_intv2_dose_mgkg',
               'sa_intv2_freq_discrete',
               'sa_intv2_dura',
              'sa_intv2_reg_detail',
              'me_diag')]


#Unique ID for every study & arm
df$id<-paste0(df$pub_id,"_",df$redcap_repeat_instance)

df$eff_arm_icure_num<-as.numeric(df$eff_arm_icure_num)
df$eff_arm_relapse_num<-as.numeric(df$eff_arm_relapse_num)
df$sa_num_followup<-as.numeric(df$sa_num_followup)

df0<-left_join(df,vl_sev,by="id")  #
colnames(relapse_def)[1]<-"pub_id"
df0<-left_join(df0,relapse_def,by="pub_id")
 
df0$tag<-NULL
df0$Arm_ID<-NULL
df0$arm_no<-NULL


length(unique(df0$pub_id))
#Subset unpublished studies
#Already removed 22 studies in Preproc!!
#182-22=160 now
df<-subset(df0,df0$st_status=="Published")
length(unique(df$pub_id))


df<-left_join(df,vl_sae,by='id')
df<-left_join(df,vl_6monthplus_relapse ,by='id')

length(unique(df0$pub_id))
length(unique(df$pub_id))
rm(vl_sev)
rm(relapse_def)
rm(df0)
rm(vl_main)



#Single drug or combination therapy. mono=1 for single drug
df$mono<-ifelse(is.na(df$sa_intv2_drug),1,0 )

#Making new treatment name
df$drug<-ifelse(df$mono==1,df$sa_intv1_drug, paste0(df$sa_intv1_drug,' & ',df$sa_intv2_drug))

#Drug list
druglist<-unique(df$drug)

#Dosage of LamB?
#Use Freq_new as orignal dosage variable has missing info.
#Freq_new created after 11_25 version

df$sd<-ifelse(df$sa_intv1_freq_new=="Single dose",1,
              ifelse(df$sa_intv1_freq_new=="Unknown",99,0))

#dcat is for LamB regimens

df$dcat<-ifelse((df$sa_intv1_drug=="Liposomal Amphotericin B (L-AmB)" & df$mono==1 & df$sd==1),"LamB SD Mono", #LamB single dose Mono
         ifelse((df$sa_intv1_drug=="Liposomal Amphotericin B (L-AmB)" & df$mono==0 & df$sd==1),"LamB SD Comb",#LamB single dose Combo
         ifelse((df$sa_intv1_drug=="Liposomal Amphotericin B (L-AmB)" & df$mono==1 & df$sd==0),"LamB MD Mono",#LamB multi dose Mono
         ifelse((df$sa_intv1_drug=="Liposomal Amphotericin B (L-AmB)" & df$mono==0 & df$sd==0),"LamB MD Comb",#LamB multi dose Combo
         ifelse((df$sa_intv1_drug=="Liposomal Amphotericin B (L-AmB)" &  df$mono==1 & df$sd==99),"LamB UD Mono",#LamB ? dose Mono
         ifelse((df$sa_intv1_drug=="Liposomal Amphotericin B (L-AmB)" &  df$mono==0 & df$sd==99),"LamB UD Comb",0))))))#LamB ? dose Combo


library(readxl)
drug_cat <- read_excel("DrugCategories.xlsx", sheet = "drug_category")
colnames(drug_cat)<-c("drug","drug_cat_others","Freq")
df1<-left_join(df,drug_cat,by='drug')
df1$Freq<-NULL
#Drugcat is final drug regimen variable
df1$drugcat<-ifelse(df1$dcat==0,df1$drug_cat_others,df1$dcat)


#Drug category list
drugcatlist<-unique(df1$drugcat)
length(unique(df1$pub_id))


#Subsetting studies with NA values

#Removing studies with no reported denominator/cured numbers and 0 cured ones
#Not removing those with NA as relapse num, because total_relapse maynot be NA

df2<-subset(df1,df1$eff_arm_icure_num>0)
length(unique(df2$pub_id))

df2$n_icured<-df2$eff_arm_icure_num
df2$eff_arm_icure_num<-NULL
#-----------------------------------------------------------------------------------------------------------------------

length(unique(df2$pub_id))
#140 studies

#Remove studies with HIV co-infections
df_all<-subset(df2,!df2$me_hiv_yn=="Yes")
length(unique(df_all$pub_id))
df_hiv<-subset(df2,df2$me_hiv_yn=="Yes")
length(unique(df_hiv$pub_id))
#124 left

#Remove studies with <6 month follow-up
df_all<-subset(df_all,!df_all$st_followup<180)
length(unique(df_all$pub_id))
table(df_all$eff_arm_relapse_days)
#----------------------------------------------------------------------------------------------------------------------------------------------------------------

#Marking ones with 180 day follow-up: Categorizing studies by measurement of relapse time: 

#1) Studies with relapse days (reported) for exact 180--                             --1--  eff_relapse_num 
#2) Studies with relapse days (reported) of >180 and info on relapse at 6 month      --2--  relapse_6+relapse_6l
#3) Studies with relapse days (reported) of >180 and no info on relapse at 6 month   --0--  NA

#Important to treat NA and 0 differently. If NA/no info at 6 months, relapse_measurement_time (rmt) cannot be 180!
#If it is 0 at 6 months, can be included, rmt can be 180

df_all$rmt180<-ifelse(df_all$eff_arm_relapse_days==180,1,
                      ifelse(df_all$eff_arm_relapse_days>180&(!is.na(df_all$relapse_6)),2,0))


#Final relapse number variable at 180 days: frel180

df_all$frel180<-ifelse(df_all$eff_arm_relapse_days==180&is.na(df_all$relapse_6_12),df_all$eff_arm_relapse_num, 
                       #180 days FU and no value for relapse at 6-12m, take main value
              ifelse(df_all$eff_arm_relapse_days==180&!is.na(df_all$relapse_6_12),rowSums(df_all[,c("relapse_6l","relapse_6")],na.rm=TRUE),
                       #180 days FU and some value for relapse at 6-12m, DO NOT take main value, take relapses till 6 months ONLY!
                                ifelse(df_all$rmt180==2,rowSums(df_all[,c("relapse_6l","relapse_6")],na.rm = TRUE),NA)))
                       #180+ days FU and relapses reported at 6m--Definitely value at relapse_6-12, take relapses till 6 months ONLY! 
                      #For those with ?180 FU, no value at 6m, NA!


#Some studies with relapse_time less than 180!! 


#Marking ones with 180-360 day follow-up: Categorizing studies by measurement of relapse time: 
#1) Studies with relapse days (reported) of >180 and info on relapse at 6-12 month              --1--  relapse_6-12 only!! DONT TAKE relapse_6!
#2) Studies with relapse days (reported) of >180 and no info on relapse at 6-12 month (NA)      --0--  NA


df_all$rmt360<-ifelse(df_all$eff_arm_relapse_days>=180&(!is.na(df_all$relapse_6_12)),1,0)

df_all$frel360<-ifelse(df_all$rmt360==1,df_all$relapse_6_12,NA)




#Converting to factors:
df_all$cases_grouped<-as.factor(df_all$cases_grouped)
df_all$cases_grouped[is.na(df_all$cases_grouped)]<-"Unclear"
df_all$severe_ka_included[is.na(df_all$severe_ka_included)]<-"Unclear"
df_all$relapse_method[is.na(df_all$relapse_method)]<-"Not defined"
df_all$relapse_method[df_all$relapse_method=="parasitological"]<-"Parasitological"
df_all$relapse_method<-as.factor(df_all$relapse_method)

df_all$n_relapse<-ifelse(df_all$eff_arm_relapse_num==0,0.5,df_all$eff_arm_relapse_num)
df_all$n_ifail<-df_all$sa_num_tx-df_all$n_icured
df_all$eff_arm_relapse_num<-NULL

df_all[,c("number_of_deaths","n_SAEs","pkdl")]<-sapply(df_all[,c("number_of_deaths","n_SAEs","pkdl")], as.numeric)
df_all<-as.data.frame(df_all)

#Defining the composite measure:Initial Failures, Relapses and deaths!!!

df_all$compo<-rowSums(df_all[,c("n_relapse","n_ifail")],na.rm = TRUE)

#Correcting relapse method
df_all$rel_diag<-ifelse(df_all$relapse_method=="clinical","C",
                        ifelse(df_all$relapse_method %in% c("clinical + parasitological","Parasitological"),"P",
                               ifelse(df_all$relapse_method %in% c("not defined","Not defined"),"U","CPS")))

df_main<-df_all
#df_main$n_relapse<-NULL

df_main$frel<-rowSums(df_main[c('frel180','frel360')],na.rm = TRUE)
#Checking how many with rmt180 and rmt360==0
#Some studies are missed this way, nmeed to put values from redcap (n_relapse)

c1<-subset(df_main,df_main$rmt180==0&df_main$rmt360==0)

df_main$rmt360n<-ifelse(df_main$rmt180==0&df_main$rmt360==0&df_main$eff_arm_relapse_days>=180,1,df_main$rmt360)
df_main$rmt180n<-ifelse(df_main$rmt180==0&df_main$rmt360==0&df_main$eff_arm_relapse_days<180,1,df_main$rmt180)

df_main$frel360n<-ifelse(df_main$rmt180==0&df_main$rmt360==0&df_main$eff_arm_relapse_days>=180,df_main$n_relapse,df_main$frel360)
df_main$frel180n<-ifelse(df_main$rmt180==0&df_main$rmt360==0&df_main$eff_arm_relapse_days<180,df_main$n_relapse,df_main$frel180)
df_main$freln<-rowSums(df_main[c('frel180n','frel360n')],na.rm = TRUE)


df_main$relapse_timen<-ifelse(df_main$rmt180==0&df_main$rmt360==0&df_main$eff_arm_relapse_days>=180,df_main$eff_arm_relapse_days,df_main$relapse_time)
table(df_main$frel-df_main$freln)
c2<-subset(df_main,df_main$rmt180n==0&df_main$rmt360n==0)

df_main$frel<-df_main$freln
df_main$frel180<-df_main$frel180n
df_main$frel360<-df_main$frel360n
df_main$rmt180<-df_main$rmt180n
df_main$rmt360<-df_main$rmt360n
df_main$relapse_time<-df_main$relapse_timen

df_main[,c("rmt180n","rmt360n","frel180n","frel360n","freln","relapse_timen")]<-NULL
df_main<-subset(df_main,!df_main$frel<0)
#120 studies!
```


Overall Meta-analysis : Subgroup analysis
```{r echo=FALSE, message=FALSE, warning=FALSE}
print("Meta-analysis overall")

df_all<-subset(df_main,!df_main$frel<0)
df_all<-subset(df_all,!is.na(df_all$n_icured))


df_all<-subset(df_main,!df_main$n_relapse<0)

m_all<- metaprop(
  data = df_all,
  event =frel,
  n=n_icured, 
  sm = "PLOGIT",
  prediction=TRUE
)
summary(m_all)

m_all.reldiag<-update.meta(m_all, 
            byvar= rel_diag,
            comb.random = TRUE, 
            comb.fixed = F)


events<-df_all%>% 
    dplyr::group_by(rel_diag) %>%
  dplyr::summarise(
    n_studies 	= length(unique(pub_id)),
    n_event	= sum(frel),
    n_cured	= sum(n_icured),
    n_totfu= sum(sa_num_tx))

m_all.intdiag<-update.meta(m_all, 
            byvar= me_diag,
            comb.random = TRUE, 
            comb.fixed = F)


events<-df_all%>% 
    dplyr::group_by(me_diag) %>%
  dplyr::summarise(
    n_studies 	= length(unique(pub_id)),
    n_event	= sum(frel),
    n_cured	= sum(n_icured),
    n_totfu= sum(sa_num_tx))


m_all.casetype<-update.meta(m_all, 
            byvar= cases_grouped,
            comb.random = TRUE, 
            comb.fixed = F)

print("Meta-analysis by Case type")
summary(m_all.casetype)

events<-df_all%>% 
    dplyr::group_by(cases_grouped) %>%
  dplyr::summarise(
    n_studies 	= length(unique(pub_id)),
    n_event	= sum(frel),
    n_cured	= sum(n_icured),
    n_totfu= sum(sa_num_tx))



m_all.drugcat<-update.meta(m_all, 
            byvar=drugcat,
            comb.random = TRUE, 
            comb.fixed = F)

print("Meta-analysis by drug Category")
summary(m_all.drugcat)

m_all.region<-update.meta(m_all, 
            byvar=st_region,
            comb.random = TRUE, 
            comb.fixed = F)

print("Meta-analysis by Region")
summary(m_all.region)



m_all.sevcases<-update.meta(m_all, 
            byvar= severe_ka_included,
            comb.random = TRUE, 
            comb.fixed = F)

print("Meta-analysis by severe case inclusion")
summary(m_all.sevcases)


m_all.relapsemethod<-update.meta(m_all, 
            byvar= relapse_method,
            comb.random = TRUE, 
            comb.fixed = F)

print("Meta-analysis by relapse method")
summary(m_all.sevcases)

```

Focus on studies with 6 month follow-up.
```{r}
#MAIN DATA SET FOR NOW!!
df_6m<-subset(df_main,df_main$rmt180>0)

c1<-subset(df_main,!df_main$rmt180>0)
df_6m<-subset(df_6m,!df_6m$n_icured>0)
#df_6m$frel<-rowSums(df_6m[c('frel180','frel360')],na.rm = TRUE)


#Overall relapse estimate at 6 months for relapse proportions

m_6m<- metaprop(
  data = df_6m,
  event =  frel180,
  n=n_icured, 
  sm = "PLOGIT",
  prediction=TRUE
)
summary(m_6m)

events_6m<-df_6m %>% 
  dplyr::summarise(
    n_studies 	= length(unique(pub_id)),
    n_event	= sum(frel180),
    n_cured	= sum(n_icured),
    n_totfu= sum(sa_num_tx))

m_6m.hiv<-update.meta(m_6m, 
            byvar=me_hiv_yn,
            comb.random = TRUE, 
            comb.fixed = F)

#No significant subgroup differences b/w unknown and no HIV studies status. 
#We continue with all of them, likely to not include when status is unknown.



#-----------
m_6m.casetype<-update.meta(m_6m, 
            byvar=cases_grouped,
            comb.random = TRUE, 
            comb.fixed = F)

summary(m_6m.casetype)

events_casetype<-df_6m %>% 
  dplyr::group_by(cases_grouped) %>%
  dplyr::summarise(
    n_studies 	= length(unique(pub_id)),
    n_event	= sum(frel180),
    n_cured	= sum(n_icured),
    n_totfu= sum(sa_num_tx))

events_casetype

m_6m.rel<-update.meta(m_6m, 
            byvar=rel_diag,
            comb.random = TRUE, 
            comb.fixed = F)

summary(m_6m.rel)

events_rel<-df_6m %>% 
  dplyr::group_by(rel_diag) %>%
  dplyr::summarise(
    n_studies 	= length(unique(pub_id)),
    n_event	= sum(frel180),
    n_cured	= sum(n_icured),
    n_totfu= sum(sa_num_tx))


m_6m.int<-update.meta(m_6m, 
            byvar=me_diag,
            comb.random = TRUE, 
            comb.fixed = F)

summary(m_6m.int)

events_int<-df_6m %>% 
  dplyr::group_by(me_diag) %>%
  dplyr::summarise(
    n_studies 	= length(unique(pub_id)),
    n_event	= sum(frel180),
    n_cured	= sum(n_icured),
    n_totfu= sum(sa_num_tx))




m_6m.sevcases<-update.meta(m_6m, 
            byvar=severe_ka_included ,
            comb.random = TRUE, 
            comb.fixed = F)

summary(m_6m.sevcases)


events_sev<-df_6m %>% 
  dplyr::group_by(severe_ka_included) %>%
  dplyr::summarise(
    n_studies 	= length(unique(pub_id)),
    n_event	= sum(frel180),
    n_cured	= sum(n_icured),
    n_totfu= sum(sa_num_tx))

```


Stratified analysis by Region and Drug categories
For all studies at 6 month follow-up!

```{r echo=TRUE, message=FALSE, warning=FALSE}
#MAIN DATA SET FOR NOW!!
df_6m<-subset(df_main,df_main$rmt180>0)
df_6m<-subset(df_6m,df_6m$n_icured>0)
df_6m<-subset(df_6m,!df_6m$st_region=="Multi-Regional")

final<-NULL

drugcatlist<- c("LamB SD Mono" ,"LamB SD Comb",  "LamB MD Mono", "LamB MD Comb", "LamB UD Mono" ,"AmphB deoxycholate" ,"AmphB (FLCC)" ,"Miltefosine","Paromomycin" ,"Miltefosine & Paromomycin" ,"PA" ,"PA & Paromomycin"  ,"PA comb")    


for (i in 1:18){
  
tmp<- df_6m[which(df_6m$drugcat==drugcatlist[i]),]

if(nrow(tmp)==0) next
tmp<- droplevels(tmp)

m<- metaprop(
  data = tmp,
  event = frel180,#Relapse variable to be considered: Here it is at 180 days
  n=n_icured, 
  sm = "PLOGIT",
  prediction=TRUE
)
assign(paste0("m_",i),m)


# Egger's test for assessing publication bias
#metabias(m)
#trimfill(m)

#--------------------------------
# Subgroup analysis by Drug category
#--------------------------------
m_region<-update.meta(m, 
            byvar=st_region, 
            comb.random = TRUE, 
            comb.fixed = F)
assign(paste0("m_region_",i),m_region)

s<-summary(m_region)
s1<-s$within.random

est<- exp(s1$TE)/(1+exp(s1$TE))
est<-round(est,4)
lb<-exp(s1$lower )/(1+exp(s1$lower))
lb<-round(lb,3)
ub<-exp(s1$upper )/(1+exp(s1$upper))
ub<-round(ub,3)

i2<-s$I2.w
i2_est<- i2$TE
i2_lb<-i2$lower
i2_ub<-i2$upper
i2_est<-round(i2_est,3)
i2_lb<-round(i2_lb,3)
i2_ub<-round(i2_ub,3)

a<-NULL
a=s$within.predict$lower
p_lb<-exp(a)/(1+exp(a))

a<-NULL
a=s$within.predict$upper
p_ub<-exp(a)/(1+exp(a))

n<-s$k.w
region<-s$bylevs
dm<-cbind(region,n,est,lb,ub,i2_est,i2_lb,i2_ub,p_lb,p_ub)
dm<-as.data.frame(dm)
dm$drugcat<-drugcatlist[i]
dm<-dm[,c(11,1:10)]

o<-s$random
o_n<-s$k
o_est<-exp(o$TE)/(1+exp(o$TE))
o_lb<-exp(o$lower)/(1+exp(o$lower))
o_ub<-exp(o$upper)/(1+exp(o$upper))


oi2<-s$I2
a<-NULL
a=s$predict$lower
o_plb<-exp(a)/(1+exp(a))
a<-NULL
a=s$predict$upper
o_pub<-exp(a)/(1+exp(a))


o_row<-round(c(o_est,o_lb,o_ub,oi2$TE,oi2$lower,oi2$upper,o_plb,o_pub),3)
o_row<-c(drugcatlist[i],"Overall",o_n, o_row)


dm<-rbind(o_row,dm)


events_region<-tmp %>% 
  dplyr::group_by(st_region) %>%
  dplyr::summarise(
    n_studies 	= length(unique(pub_id)),
    n_event	= sum(frel180), #Relapse variable to be considered: Here it is at 180 days
    n_cured	= sum(n_icured),
    n_totfu= sum(sa_num_tx))
colnames(events_region)[1]<-"region"


dm<-left_join(dm,events_region,by='region')

final<-rbind(final,dm)
assign(paste0("dm_",i),dm)
 
print(drugcatlist[i])
print(s)
}

final_store_rel<-final
drugcat_names <- read_excel("DrugCategories.xlsx", 
    sheet = "drug cat full names")

final<-left_join(final,drugcat_names,by="drugcat")

final<-final[,c("Drug Category", "region",  "n_studies","n","n_totfu","n_cured","n_event","est", "lb","ub","i2_est","i2_lb","i2_ub","p_lb","p_ub")]



colnames(final)<-c("Drug Category","Region","Studies","Arms","Tot FU","In. cured", "Relapses", "Est","lb","ub","I2","i2_lb","i2_ub","p_lb","p_ub")


cols.num <- c( "Est","lb","ub","I2","i2_lb","i2_ub","p_lb","p_ub")
final[cols.num] <- sapply(final[cols.num],as.numeric)
final[, cols.num] <- lapply(final[, cols.num, drop = FALSE],
                             function(x) x * 100)

final[, cols.num] <- lapply(final[, cols.num, drop = FALSE],
                             function(x) round(x,2))
write.csv(final,"MA_drugcat_region_6m_1207.csv")#Change date and name
#Do prop.test for i=4 and 7 (Med)
#Manualy updated results in Excel
```



Plot

```{r}
library(readxl)
res_6m <- read_excel("MA_drugcat_region_6m_1207.xlsx", 
    sheet = "MA_drugcat_region_6m_1207")

colnames(res_6m)<-c("drug_category", "region",  "n_studies","arms","n_totfu","n_cured","n_event","est", "lb","ub","i2_est","i2_lb","i2_ub","p_lb","p_ub")
res_6m$id<-paste0(res_6m$drug_category,res_6m$region)

# Make every country unique
res_6m$region<-factor(res_6m$region,levels = c(  "Mediterranean","Central Asia" , "South America","Eastern Africa","India Subcontinent","Overall"   ))

r<-subset(res_6m,res_6m$drug_category%in% c("LAmB (Single dose) Mono regimen"   , "LamB (Single dose) Combination regimen"  ,"LamB (Multiple dose) Mono regimen" ))
r$region<-factor(r$region,levels = c( "Mediterranean","Central Asia" , "South America","Eastern Africa","India Subcontinent","Overall"   ))


library(RColorBrewer)

#define custom color scale
myColors <- brewer.pal(6, "Dark2")
names(myColors) <- levels(r$region)
myColors[6]<-"#E7298A"
myColors[4]<- "#1E3F66"
custom_colors <- scale_colour_manual(values = myColors)

p <- ggplot(r, aes(x=region, y=est, ymin=lb, ymax=ub,colour = region)) + geom_pointrange( size=1.05,aes(colour = region))+
#+ coord_cartesian(ylim=c(0, 30))+
  coord_flip()+ ylab("Relapse Proportion at 6month (%)")+xlab("")+labs("Region")+
  facet_wrap(~ drug_category, ncol = 1) +  theme(panel.background = element_rect(fill = "white"),panel.grid.major = element_line("lightgray",0.5),
        panel.grid.minor = element_line("lightgray",0.25))+ custom_colors




r1<-subset(res_6m,res_6m$drug_category%in% c("Amphotericin B deoxycholate"  , "Amphotericin b (fat/lipid/colloid/cholestrol)"))

p1 <- ggplot(r1, aes(x=region, y=est, ymin=lb, ymax=ub,colour = region)) + geom_pointrange( size=1.05,aes(colour = region))+
#+ coord_cartesian(ylim=c(0, 30))+
  coord_flip()+ ylab("Relapse Proportion at 6month (%)")+xlab("")+labs("Region")+
  facet_wrap(~ drug_category, ncol = 1) +  theme(panel.background = element_rect(fill = "white"),panel.grid.major = element_line("lightgray",0.5),
        panel.grid.minor = element_line("lightgray",0.25))+ custom_colors
p1

ann_text <- data.frame(mpg = 15,wt = 5,lab = "Text",
                       cyl = factor(8,levels = c("4","6","8")))
p + geom_text(data = ann_text,label = "Text")

r2<-subset(res_6m,res_6m$drug_category %in% c("Miltefosine"  ,"Paromomycin","Miltefosine & Paromomycin"  ,"Pentavalent antimonial" , "Pentavalent antimonial+ Paromomycin"))

p2 <- ggplot(r2, aes(x=region, y=est, ymin=lb, ymax=ub,colour = region)) + geom_pointrange( size=1.05,aes(colour = region))+
#+ coord_cartesian(ylim=c(0, 30))+
  coord_flip()+ ylab("Relapse Proportion at 6month (%)")+xlab("")+labs("Region")+
  facet_wrap(~ drug_category, ncol = 1) +  theme(panel.background = element_rect(fill = "white"),panel.grid.major = element_line("lightgray",0.5),
        panel.grid.minor = element_line("lightgray",0.25))+ custom_colors
p


```

PLotting for Treatment failure measure!!

```{r echo=TRUE, message=FALSE, warning=FALSE}
#MAIN DATA SET FOR NOW!!
df_6m<-subset(df_main,df_main$rmt180>0)
df_6m<-subset(df_6m,df_6m$n_icured>0)
df_6m<-subset(df_6m,!df_6m$st_region=="Multi-Regional")

final<-NULL

drugcatlist<- c("LamB SD Mono" ,"LamB SD Comb",  "LamB MD Mono", "LamB MD Comb", "LamB UD Mono" ,"AmphB deoxycholate" ,"AmphB (FLCC)" ,"Miltefosine","Paromomycin" ,"Miltefosine & Paromomycin" ,"PA" ,"PA & Paromomycin"  ,"PA comb")    


for (i in 1:18){
  
tmp<- df_6m[which(df_6m$drugcat==drugcatlist[i]),]

if(nrow(tmp)==0) next
tmp<- droplevels(tmp)

m<- metaprop(
  data = tmp,
  event = compo,#Relapse variable to be considered: Here it is at composite measure
  n=sa_num_tx, 
  sm = "PLOGIT",
  prediction=TRUE
)
#assign(paste0("m_",i),m)


# Egger's test for assessing publication bias
#metabias(m)
#trimfill(m)

#--------------------------------
# Subgroup analysis by Drug category
#--------------------------------
m_region<-update.meta(m, 
            byvar=st_region, 
            comb.random = TRUE, 
            comb.fixed = F)
#assign(paste0("m_region_",i),m_region)

s<-summary(m_region)
s1<-s$within.random

est<- exp(s1$TE)/(1+exp(s1$TE))
est<-round(est,4)
lb<-exp(s1$lower )/(1+exp(s1$lower))
lb<-round(lb,3)
ub<-exp(s1$upper )/(1+exp(s1$upper))
ub<-round(ub,3)

i2<-s$I2.w
i2_est<- i2$TE
i2_lb<-i2$lower
i2_ub<-i2$upper
i2_est<-round(i2_est,3)
i2_lb<-round(i2_lb,3)
i2_ub<-round(i2_ub,3)

a<-NULL
a=s$within.predict$lower
p_lb<-exp(a)/(1+exp(a))

a<-NULL
a=s$within.predict$upper
p_ub<-exp(a)/(1+exp(a))

n<-s$k.w
region<-s$bylevs
dm<-cbind(region,n,est,lb,ub,i2_est,i2_lb,i2_ub,p_lb,p_ub)
dm<-as.data.frame(dm)
dm$drugcat<-drugcatlist[i]
dm<-dm[,c(11,1:10)]

o<-s$random
o_n<-s$k
o_est<-exp(o$TE)/(1+exp(o$TE))
o_lb<-exp(o$lower)/(1+exp(o$lower))
o_ub<-exp(o$upper)/(1+exp(o$upper))


oi2<-s$I2
a<-NULL
a=s$predict$lower
o_plb<-exp(a)/(1+exp(a))
a<-NULL
a=s$predict$upper
o_pub<-exp(a)/(1+exp(a))


o_row<-round(c(o_est,o_lb,o_ub,oi2$TE,oi2$lower,oi2$upper,o_plb,o_pub),3)
o_row<-c(drugcatlist[i],"Overall",o_n, o_row)


dm<-rbind(o_row,dm)


events_region<-tmp %>% 
  dplyr::group_by(st_region) %>%
  dplyr::summarise(
    n_studies 	= length(unique(pub_id)),
    n_event	= sum(compo), #Relapse variable to be considered: Here it is at 180 days
    n_cured	= sum(n_icured),
    n_totfu= sum(sa_num_tx))
colnames(events_region)[1]<-"region"


dm<-left_join(dm,events_region,by='region')

final<-rbind(final,dm)
assign(paste0("dm_",i),dm)
 
print(drugcatlist[i])
print(s)
}

final_store<-final
drugcat_names <- read_excel("DrugCategories.xlsx", 
    sheet = "drug cat full names")

final<-left_join(final,drugcat_names,by="drugcat")

final<-final[,c("Drug Category", "region",  "n_studies","n","n_totfu","n_cured","n_event","est", "lb","ub","i2_est","i2_lb","i2_ub","p_lb","p_ub")]



colnames(final)<-c("Drug Category","Region","Studies","Arms","Tot FU","In. cured", "TFs", "Est","lb","ub","I2","i2_lb","i2_ub","p_lb","p_ub")

cols.num <- c( "Est","lb","ub","I2","i2_lb","i2_ub","p_lb","p_ub")
final[cols.num] <- sapply(final[cols.num],as.numeric)
final[, cols.num] <- lapply(final[, cols.num, drop = FALSE],
                             function(x) x * 100)

final[, cols.num] <- lapply(final[, cols.num, drop = FALSE],
                             function(x) round(x,2))
write.csv(final,"MA_drugcat_region_6m_compo_1207.csv")#Change date and name
```


Focus on 13 studies with follow up duration of more than 6 months
```{r}
df_13<-subset(df_main,df_main$rmt360==1)

#df_13f<-subset(df_13,!df_13$drugcat%in%c("AmphB (Unk)","Sitamaquine",  "Others"))

df12m<-subset(df_13,!df_13$relapse_time%in% c("240","270"))
#Only studies with estiamtes at 6 and 12 months both!!
df612<-subset(df12m,df12m$rmt180>0)
length(unique(df612$pub_id))
#Estimate at 6 month only
m6<- metaprop(
  data = df612,
  event =  frel180,
  n=n_icured, 
  sm = "PLOGIT",
  prediction=TRUE)

events<-df612 %>% 
  dplyr::summarise(
    n_studies 	= length(unique(pub_id)),
    n_event	= sum(frel180), #Relapse variable to be considered: Here it is at 180 days
    n_cured	= sum(n_icured),
    n_totfu= sum(sa_num_tx))

#Estimate at 12 month only
m12<- metaprop(
  data = df612,
  event =  frel360,
  n=n_icured, 
  sm = "PLOGIT",
  prediction=TRUE)

events<-df612 %>% 
  dplyr::summarise(
    n_studies 	= length(unique(pub_id)),
    n_event	= sum(frel360), #Relapse variable to be considered: Here it is at 180 days
    n_cured	= sum(n_icured),
    n_totfu= sum(sa_num_tx))

#Estimate at 12 month only
m612<- metaprop(
  data = df612,
  event =  frel,
  n=n_icured, 
  sm = "PLOGIT",
  prediction=TRUE)

events<-df612 %>% 
  dplyr::summarise(
    n_studies 	= length(unique(pub_id)),
    n_event	= sum(frel), #Relapse variable to be considered: Here it is at 180 days
    n_cured	= sum(n_icured),
    n_totfu= sum(sa_num_tx))



m13s_12<-update.meta(m13_12, 
            byvar=pub_id, 
            comb.random = TRUE, 
            comb.fixed = F)

events<-df_13 %>% 
  dplyr::group_by(pub_id) %>%
  dplyr::summarise(
    n_studies 	= length(unique(pub_id)),
    n_event	= sum(frel360), #Relapse variable to be considered: Here it is at 180 days
    n_cured	= sum(n_icured),
    n_totfu= sum(sa_num_tx))

#Sum of relapses at 6 and ?6 months. If one is NA--> treated as 0
#Useless measure

#For 12 months follow up studies, not <12 but at 12 months!!
#Relapse_time is a confusing variable: Puts noted relapse cases, it is NOT FOLLOW UP DURATION!!!
#eff_relapse_days is not correctly written either.

#For now, all studies with rmt360==1 and relapse_time =! 240,270

df12m<-subset(df_13,!df_13$relapse_time%in% c("240","270"))
length(unique(df12m$pub_id))
#11 studies with 12 month follow-up and reporting at 12 months
m11<- metaprop(
  data = df12m,
  event =  frel,
  n=n_icured, 
  sm = "PLOGIT",
  prediction=TRUE)

summary(m11)
#-------------
#Relapse at 6 months Estimate:

m11_6<- metaprop(
  data = df12m,
  event =  frel180,
  n=n_icured, 
  sm = "PLOGIT",
  prediction=TRUE)

summary(m11_6)


events_m11_6<-df12m %>% 
  dplyr::summarise(
    n_studies 	= length(unique(pub_id)),
    n_event	= sum(frel180,na.rm = TRUE),
    n_cured	= sum(n_icured),
    n_totfu= sum(sa_num_tx))

events_m11_drug<-df12m %>% 
  dplyr::group_by(drugcat) %>%
  dplyr::summarise(
    n_studies 	= length(unique(pub_id)),
    n_event	= sum(frel180,na.rm = TRUE),
    n_cured	= sum(n_icured),
    n_totfu= sum(sa_num_tx))



m11_12<- metaprop(
  data = df12m,
  event =  frel360,
  n=n_icured, 
  sm = "PLOGIT",
  prediction=TRUE)

summary(m13_12)

events_m13_12<-df12m%>% 
  dplyr::summarise(
    n_studies 	= length(unique(pub_id)),
    n_event	= sum(frel360,na.rm = TRUE),
    n_cured	= sum(n_icured),
    n_totfu= sum(sa_num_tx))

```

For Indian Subcontinent, LamB SD: DOsage and relapse relationship

```{r}
df_ind<-subset(df_main,df_main$st_region=="India Subcontinent")
df_ind$sa_int1_total_dose<-as.numeric(df_ind$sa_int1_total_dose)

df_ind1<-subset(df_ind,df_ind$drugcat=="LamB SD Mono")
df_ind1<-subset(df_ind1,df_ind1$frel180>=0)

df_ind1$sa_int1_total_dose<-as.numeric(df_ind1$sa_int1_total_dose)
df_ind1$total_dose<-ifelse(df_ind1$sa_int1_total_dose<=5,1,ifelse(df_ind1$sa_int1_total_dose<=10,2,3))
table(df_ind1$sa_int1_total_dose)
table(df_ind1$total_dose)


m<- metaprop(
  data = df_ind1,
  event = compo,
  n=sa_num_tx, 
  sm = "PLOGIT",
  prediction=TRUE
)
summary(m)
m.dose<-update.meta(m, 
            byvar=total_dose,
            comb.random = TRUE, 
            comb.fixed = F)
summary(m.dose)

events<-df_ind1%>% 
    dplyr::group_by(total_dose) %>%
   dplyr::summarise(
    n_studies 	= length(unique(pub_id)),
    n_event	= sum(compo,na.rm = TRUE),
    n_cured	= sum(n_icured),
    n_totfu= sum(sa_num_tx))

#Performs chi-squared test for trend in proportion. This test is also known as Cochran-Armitage trend test.
#Wrappers around the R base function prop.trend.test() but returns a data frame for easy data visualization.


df_ind1$n_defcure<-df_ind1$n_icured-df_ind1$frel180
df_ind1$notf<-df_ind1$sa_num_tx-df_ind1$compo

xtab<-as.table(cbind(df_ind1$frel180,df_ind1$n_defcure))
xtab1<-as.table(cbind(df_ind1$compo,df_ind1$notf))

library('rstatix')
prop_trend_test(xtab,df_ind1$total_dose)

prop_trend_test(xtab1,df_ind1$total_dose)

```

```{r}
library('lme4')
model1<- glmer(cbind(frel180,n_defcure) ~   sa_int1_total_dose + (1 | id) ,
              family = binomial, data = df_ind1)

summary(model1)


model1a<- glmer(cbind(frel180,n_defcure) ~   sa_int1_total_dose +rel_diag+(1 | id) ,
              family = binomial, data = df_ind1)

summary(model1a)


model2<- glmer(cbind(compo,notf) ~   sa_int1_total_dose + (1 | id) ,
              family = binomial, data = df_ind1)

summary(model2)
```


```{r}
df_ea<-subset(df_main,df_main$st_region=="Eastern Africa")
df_ea$sa_int1_total_dose<-as.numeric(df_ea$sa_int1_total_dose)

df_ea<-subset(df_ea,df_ea$drugcat=="LamB SD Mono")
df_ind1<-subset(df_ind1,df_ind1$frel180>=0)
```


```{r}

```

