---
output:
  word_document: default
  html_document: default
---
VL Relapse analysis 15 Dec 2021

PRE-PROCESSING THE FINAL DATASET FOR ANALYSIS:

I)Creating drug classes, follow up duration related variables.
II) Adding residuals to 0 event studies
III) Filtering out studies:
  1. Removing HIV co-infection based studies
  2. Missing info
  3. < 6month follow-up
  4. Unpublished (already removed)

```{r message=FALSE, warning=FALSE, include=FALSE}

library(readr)
library(readxl)
# meta-analysis packages
library(meta)
library(metafor)
#library(metagen)
library(metasens) 
# graphics packages
library(tidyverse)
library(reshape)
library(doBy)
library(stringr)
library(ggpubr)
library(patchwork)
library(dplyr)
library(data.table)
setwd("C:/Users/Rutuja Chhajed/OneDrive - Nexus365/IDDO/Data")

#D1: VLDATA_CLEAN
#Pre-processed data (see Prepoc.R for the steps)
#Pick up latest cleaned file
#Check OneNote for the latest version
vl_main <-read_csv("VL_cleandata_0222.csv")
length(unique(vl_main$pub_id)) #160 studies!

#Additional variables from the vl_studydesign: Relapse definitions, severe cases inclusion, type if VL cases.
#D2: VL_SEVEREDESIGN
relapse_def <- read_excel("vl_studydesign.xlsx", 
    sheet = "outcome_defintion", col_types = c("numeric", 
        "skip", "skip", "text", "text"))

relapse_def$relapse_method<-tolower(relapse_def$relapse_method)

vl_sev <- read_excel("vl_studydesign.xlsx", 
    sheet = "disease_severity", col_types = c("skip", 
        "numeric", "skip", "numeric", "skip", 
        "text", "numeric", "skip", "text", 
        "skip", "text"))
#Dont change order in the raw excel file


setwd("C:/Users/Rutuja Chhajed/OneDrive - Nexus365/IDDO/Data")
drug_cat <- read_excel("DrugCategories.xlsx", sheet = "drug_category")

setDT(vl_sev)[, arm_no := rowid(tag)]
vl_sev$id<-paste0(vl_sev$tag,"_",vl_sev$arm_no)
vl_sev$tag<-NULL
vl_sev$Arm_ID<-NULL
vl_sev$arm_no <-NULL


#D3: VL_SAE (Taken from SAE paper)

vl_sae <- read_excel("VL_SAE.xlsx", sheet = "VL_SAEs_per_arm_04_12_2019", 
col_types = c("skip", "skip", "skip", 
   "numeric", "skip", "numeric", "skip", 
       "skip", "skip", "skip", "skip", "text", 
       "skip", "skip", "numeric", "numeric", 
        "skip", "skip", "skip", "skip", "skip"))

vl_sae$id<-paste0(vl_sae$Tag,"_",vl_sae$Repeat.Instance )
vl_sae$Tag<-NULL
vl_sae$Repeat.Instance<-NULL

setwd("C:/Users/Rutuja Chhajed/OneDrive - Nexus365/IDDO/Data")
drug_cat <- read_excel("DrugCategories.xlsx", sheet = "drug_category")

df<-vl_main[,c('pub_id',
               'st_intv_arms',
               'redcap_repeat_instance',
               'st_followup',
               'me_hiv_yn',
               'eff_arm_icure_num',
               'eff_arm_icure_days',
               'eff_arm_relapse_num',
               'eff_arm_relapse_days',
               'st_status',
               'st_design',
               'st_allocation',
               'st_region',
               'sa_num_tx'	,
               'sa_num_followup',
               'sa_intv1_drug',
               'sa_intv1_dose_mgkg',
               'sa_intv1_freq_discrete',
               'sa_intv1_freq_new',
               'sa_int1_total_dose',
               'sa_intv1_dura',
               'sa_intv1_reg_detail' ,
               'sa_intv2_drug',
               'sa_intv2_dose_mgkg',
               'sa_intv2_freq_discrete',
               'sa_intv2_dura',
               'sa_intv2_reg_detail',
               "total_relapse",
               "relapse_6l", "relapse_6","relapse_6_12","issue","relapse_time")]

#combining all variables in one df
#Unique ID for every study & arm
df$id<-paste0(df$pub_id,"_",df$redcap_repeat_instance)
df<-left_join(df,vl_sae,by='id')
df0<-left_join(df,vl_sev,by="id")  
colnames(relapse_def)[1]<-"pub_id"
df0<-left_join(df0,relapse_def,by="pub_id")
 
df0$tag<-NULL
df0$Arm_ID<-NULL
df0$arm_no<-NULL
length(unique(df0$pub_id))
```


#2) Subsetting studies 
with NA values
Removing studies with no reported denominator/cured numbers and 0 cured ones
Not removing those with NA as relapse num, because total_relapse (Manually created variable by RC) may not be NA
```{r}

#Subset unpublished studies-------------------------------------------------------------------------------------------------------
#1) Already removed 22 studies in Preproc!!
#182-22=160 now
rm(df)
df<-subset(df0,df0$st_status=="Published")
length(unique(df$pub_id))


length(unique(df0$pub_id))
length(unique(df$pub_id))
rm(vl_sev)
rm(relapse_def)
rm(df0)
rm(vl_main)

#2) Unavailable denominator 
df1<-subset(df,df$eff_arm_icure_num>0)
length(unique(df1$pub_id))
#140 left
df1$n_icured<-df1$eff_arm_icure_num
df1$eff_arm_icure_num<-NULL

# 3) #Remove studies with HIV co-infections
df_all<-subset(df1,!df1$me_hiv_yn=="Yes")
length(unique(df_all$pub_id))
df_hiv<-subset(df1,df1$me_hiv_yn=="Yes")
length(unique(df_hiv$pub_id))
#124 left

#Remove studies with <6 month follow-up
df<-subset(df_all,!df_all$st_followup<180)
length(unique(df$pub_id))
table(df$eff_arm_relapse_days)
table(df$eff_arm_relapse_num)
#121 left
rm(df_all)
df_store<-df
```
Drug classifications:

```{r}
#Single drug or combination therapy. mono=1 for single drug
df$mono<-ifelse(is.na(df$sa_intv2_drug),1,0)

#Making new treatment name
df$drug<-ifelse(df$mono==1,df$sa_intv1_drug, paste0(df$sa_intv1_drug,' & ',df$sa_intv2_drug))

#Drug list
druglist<-unique(df$drug)

#Dosage of LamB?
#Use Freq_new as original dosage variable has missing info.
#Freq_new created after 11_25 version based on checkinh dose information manually

df$sd<-ifelse(df$sa_intv1_freq_new=="Single dose",1,
              ifelse(df$sa_intv1_freq_new=="Unknown",99,0))

#Variable dcat is for LamB regimens

df$dcat<-ifelse((df$sa_intv1_drug=="Liposomal Amphotericin B (L-AmB)" & df$mono==1 & df$sd==1),"LamB SD Mono", #LamB single dose Mono
         ifelse((df$sa_intv1_drug=="Liposomal Amphotericin B (L-AmB)" & df$mono==0 & df$sd==1),"LamB SD Comb",#LamB single dose Combo
         ifelse((df$sa_intv1_drug=="Liposomal Amphotericin B (L-AmB)" & df$mono==1 & df$sd==0),"LamB MD Mono",#LamB multi dose Mono
         ifelse((df$sa_intv1_drug=="Liposomal Amphotericin B (L-AmB)" & df$mono==0 & df$sd==0),"LamB MD Comb",#LamB multi dose Combo
         ifelse((df$sa_intv1_drug=="Liposomal Amphotericin B (L-AmB)" &  df$mono==1 & df$sd==99),"LamB UD Mono",#LamB ? dose Mono
         ifelse((df$sa_intv1_drug=="Liposomal Amphotericin B (L-AmB)" &  df$mono==0 & df$sd==99),"LamB UD Comb",0))))))#LamB ? dose Combo



colnames(drug_cat)<-c("drug","drug_cat_others","Freq")
#Combining with formal list of drug categories
df_all<-left_join(df,drug_cat,by='drug')
df_all$Freq<-NULL
#Drugcat is final drug regimen variable
df_all$drugcat<-ifelse(df_all$dcat==0,df_all$drug_cat_others,df_all$dcat)


#Drug category list
drugcatlist<-unique(df_all$drugcat)
length(unique(df_all$pub_id))

```

Separating relapses at 6 month and later. 
Creating new variables to mark that. 
Using our variables we manually filled relapses at 6l, 6 and 6p)
~Studies saying follow-up time of 12 months: Need to separate relapses at 6 month and post 6 months
~Studies saying follow-up of 12 months but relapses at 6 month only: use the data filled by RC/PD
~Incorrect numbers: Corrected by RC/PD, to be overwritten.
```{r}
#Marking ones with 180 day follow-up: Categorizing studies by measurement of relapse time: 

#1) Studies with relapse days (reported) for exact 180--                             --1--  eff_relapse_num 
#2) Studies with relapse days (reported) of >180 and info on relapse at 6 month      --2--  relapse_6+relapse_6l
#3) Studies with relapse days (reported) of >180 and no info on relapse at 6 month   --0--  NA

#Important to treat NA and 0 differently. If NA/no info at 6 months, relapse_measurement_time (rmt) cannot be 180!
#If it is 0 at 6 months, can be included, rmt can be 180

df_all$rmt180<-ifelse(df_all$eff_arm_relapse_days==180&is.na(df_all$relapse_6_12),1,
                      ifelse(df_all$eff_arm_relapse_days>180&(!is.na(df_all$relapse_6)),2,
                             ifelse(df_all$eff_arm_relapse_days==180& (!is.na(df_all$relapse_6_12)),2,0 )))


#Final relapse number variable at 180 days: frel180

df_all$frel180<-ifelse(df_all$eff_arm_relapse_days==180&is.na(df_all$relapse_6_12),df_all$eff_arm_relapse_num, 
          #1.180 days FU and no value for relapse at 6-12m, take main value
        ifelse(df_all$eff_arm_relapse_days==180&!is.na(df_all$relapse_6_12),rowSums(df_all[,c("relapse_6l","relapse_6")],na.rm=TRUE),
          #2.180 days FU and some value for relapse at 6-12m, DO NOT take main value, take relapses till 6 months ONLY!
        ifelse(df_all$rmt180==2,rowSums(df_all[,c("relapse_6l","relapse_6")],na.rm = TRUE),NA)))
        #3.#180+ days FU and relapses reported at 6m--Definitely value at relapse_6-12, take relapses till 6 months ONLY! 
          #For those with >180 FU, no value at 6m, NA! (rmt==0)


#Some studies with relapse_time less than 180!! No: removed already!


#Marking ones with 180-360 day follow-up: Categorizing studies by measurement of relapse time: 
#1) Studies with relapse days (reported) of >180 and info on relapse at 6-12 month              --1--  relapse_6-12 only!! DONT TAKE relapse_6!
#2) Studies with relapse days (reported) of >180 and no info on relapse at 6-12 month (NA)      --0--  NA


df_all$rmt360<-ifelse(df_all$eff_arm_relapse_days>=180&(!is.na(df_all$relapse_6_12)),1,0)

df_all$frel360<-ifelse(df_all$rmt360==1,df_all$relapse_6_12,NA)




#Converting to factors, changing group names.

df_all$cases_grouped<-as.factor(df_all$cases_grouped)
df_all$cases_grouped[is.na(df_all$cases_grouped)]<-"Unclear"
df_all$severe_ka_included[is.na(df_all$severe_ka_included)]<-"Unclear"
df_all$relapse_method[is.na(df_all$relapse_method)]<-"Not defined"
df_all$relapse_method[df_all$relapse_method=="parasitological"]<-"Parasitological"
df_all$relapse_method<-as.factor(df_all$relapse_method)


# Adding 0.5 to 0 relapse studies
df_all$n_relapse<-ifelse(df_all$eff_arm_relapse_num==0,0.5,df_all$eff_arm_relapse_num)
df_all$n_ifail<-df_all$sa_num_tx-df_all$n_icured
df_all$eff_arm_relapse_num<-NULL

df_all[,c("number_of_deaths","n_SAEs")]<-sapply(df_all[,c("number_of_deaths","n_SAEs")], as.numeric)
df_all<-as.data.frame(df_all)

#Defining the composite measure:Initial Failures, Relapses and deaths!!!

df_all$compo<-rowSums(df_all[,c("n_relapse","n_ifail")],na.rm = TRUE)

#Correcting relapse method
df_all$rel_diag<-ifelse(df_all$relapse_method=="clinical","C",
                        ifelse(df_all$relapse_method %in% c("clinical + parasitological","Parasitological"),"P",
                               ifelse(df_all$relapse_method %in% c("not defined","Not defined"),"U","CPS")))

df_main<-df_all
#df_main$n_relapse<-NULL


#frel will have total number of relapses
df_main$frel<-rowSums(df_main[c('frel180','frel360')],na.rm = TRUE)
df_main$frel<-ifelse(is.na(df_main$frel180)&is.na(df_main$frel360),NA,df_main$frel) #To ensure NA+NA is not 0!
```

Studies with issues: 
1. Ones with mismatch of follow-up times nad relapse numbers.
2. Incorrect numbers reported


```{r}

#Checking how many with rmt180 and rmt360==0
#Some studies are missed this way, need to put values from redcap (n_relapse)

c1<-subset(df_main,df_main$rmt180==0&df_main$rmt360==0)
c11<-subset(c1,c1$eff_arm_relapse_days>180) #Check these studies. Relapse days written as >180 in redcap, and we are taking it as it is. 
#Logic: If eff_relapse_days written incorrectly as >180,?

df_main$rmt360n<-ifelse(df_main$rmt180==0&df_main$rmt360==0&df_main$eff_arm_relapse_days>180,1,df_main$rmt360)
df_main$rmt180n<-ifelse(df_main$rmt180==0&df_main$rmt360==0&df_main$eff_arm_relapse_days<180,1,df_main$rmt180)

df_main$frel360n<-ifelse(df_main$rmt180==0&df_main$rmt360==0&df_main$eff_arm_relapse_days>180,df_main$n_relapse,df_main$frel360)
df_main$frel180n<-ifelse(df_main$rmt180==0&df_main$rmt360==0&df_main$eff_arm_relapse_days<180,df_main$n_relapse,df_main$frel180)
df_main$freln<-rowSums(df_main[c('frel180n','frel360n')],na.rm = TRUE)


df_main$relapse_timen<-ifelse(df_main$rmt180==0&df_main$rmt360==0&df_main$eff_arm_relapse_days>180,df_main$eff_arm_relapse_days,df_main$relapse_time)
table(df_main$frel-df_main$freln)
c2<-subset(df_main,df_main$rmt180n==0&df_main$rmt360n==0)

df_main$frel<-df_main$freln
df_main$frel180<-df_main$frel180n
df_main$frel360<-df_main$frel360n
df_main$rmt180<-df_main$rmt180n
df_main$rmt360<-df_main$rmt360n
df_main$relapse_time<-df_main$relapse_timen

df_main[,c("rmt180n","rmt360n","frel180n","frel360n","freln","relapse_timen")]<-NULL
df_main<-subset(df_main,!df_main$frel<0)
length(unique(df_main$pub_id))
#120 studies!

#Only for studies with issue=NM, replace the rel with those written manually (relapse_6, relapse_6-12)
#For others (Match or NA values (unverified vlaues, keep it the same!))
#Be careful about the use of NAs in inelse statements.

df_main$frel180n<-ifelse((!df_main$issue=="NM"| is.na(df_main$issue)),df_main$frel180,rowSums(df_main[,c("relapse_6l","relapse_6")]))


df_main$frel360n<-ifelse((!df_main$issue=="NM"| is.na(df_main$issue)),df_main$frel360,df_main$relapse_6_12)
df_main$freln<-rowSums(df_main[c('frel180n','frel360n')],na.rm = TRUE)

df_main$frel<-df_main$freln
df_main$frel180<-df_main$frel180n
df_main$frel360<-df_main$frel360n
df_main[,c("frel180n","frel360n","freln")]<-NULL


df_final<-subset(df_main,!df_main$frel<0)

df_final$n_relapse<-NULL
df_final$dcat<-NULL
df_final$drug_cat_others<-NULL
df_final$drug_group<-NULL
df_final$drug_group_for_analysis
saveRDS(df_final,'vl_final.RDS')
rm(df_all)
rm(df)
rm(df1)
rm(c1)
rm(c2)
```








