Analysis and results:

Function to extract results:
```{r Function: m_extract}

#Extract estimates from the copas object.
#Make a function: Input= Copas object; Output data frame

m_extract<-function(m_adj,catname){
  
  
#0) Orignal estiamte: 
est0<-exp(m_adj$TE.random)/(1+exp(m_adj$TE.random))
#2. Lower and upper bound
lb0<-exp(m_adj$lower.random)/(1+exp(m_adj$lower.random))
ub0<-exp(m_adj$upper.random)/(1+exp(m_adj$upper.random))

#1. Estimate
est<-exp(m_adj$TE.adjust)/(1+exp(m_adj$TE.adjust))
#2. Lower and upper bound
lb<-exp(m_adj$lower.adjust)/(1+exp(m_adj$lower.adjust))
ub<-exp(m_adj$upper.adjust)/(1+exp(m_adj$upper.adjust))

#3. I2 value
i2<-m_adj$x$I2

#4. Lower and upper bound for I2
i2lb<-m_adj$x$lower.I2
i2ub<-m_adj$x$upper.I2

#5. Calculation of prediction interval
#se<-m_adj$seTE.adjust

#pilb<-est-t*sqrt(i2^2+se^2)

#Total no of studies
n<-length(unique(m_adj$x$data$pub_id))

arms<-length(m_adj$x$data$pub_id)
#Total study arms

#Total patients
tot<-sum(m_adj$x$data$sa_num_tx,na.rm = TRUE )

#Total cured
tot_cured<-sum(m_adj$x$data$n_icured,na.rm = TRUE )

#Total relapsed
tot_rel<-sum(m_adj$x$data$frel180 ,na.rm = TRUE )

 
op<-as.data.frame(t(as.data.frame(c(est0, lb0, ub0, est, lb, ub, i2, i2lb, i2ub, n, arms, tot, tot_cured, tot_rel))))
colnames(op)<-c("est0","lb0","ub0","est","lb","ub","i2","i2lb","i2ub","n","arms","tot", "cured","relapse")
rownames(op)<-NULL


op <- sapply(op,as.numeric)
op <- sapply(op, function(x) round(x,4))

op<-as.data.frame(t(op))
op$name<-catname

return(op)
}

```

```{r Function: m_extract0}

#Extract estimates from the copas object.
#Make a function: Input= Copas object; Output data frame

m_extract0<-function(m_unadj,catname){
  
  
#0) Orignal estiamte: 
est0<-exp(m_unadj$TE.random)/(1+exp(m_unadj$TE.random))
#2. Lower and upper bound
lb0<-exp(m_unadj$lower.random)/(1+exp(m_unadj$lower.random))
ub0<-exp(m_unadj$upper.random)/(1+exp(m_unadj$upper.random))

#1. Estimate
#est<-exp(m_unadj$TE.adjust)/(1+exp(m_unadj$TE.adjust))
#2. Lower and upper bound
#lb<-exp(m_unadj$lower.adjust)/(1+exp(m_unadj$lower.adjust))
#ub<-exp(m_unadj$upper.adjust)/(1+exp(m_unadj$upper.adjust))

#3. I2 value
i2<-m_unadj$I2

#4. Lower and upper bound for I2
i2lb<-m_unadj$lower.I2
i2ub<-m_unadj$upper.I2

#5. Calculation of prediction interval
#se<-m_unadj$seTE.adjust

#pilb<-est-t*sqrt(i2^2+se^2)

#Total no of studies
n<-length(unique(m_unadj$data$pub_id))

arms<-length(m_unadj$data$pub_id)
#Total study arms

#Total patients
tot<-sum(m_unadj$data$sa_num_tx,na.rm = TRUE )

#Total cured
tot_cured<-sum(m_unadj$data$n_icured,na.rm = TRUE )

#Total relapsed
tot_rel<-sum(m_unadj$data$frel180 ,na.rm = TRUE )

est<-99
lb<-99
ub<-99
op<-as.data.frame(t(as.data.frame(c(est0, lb0, ub0, est, lb, ub, i2, i2lb, i2ub, n, arms, tot, tot_cured, tot_rel))))
colnames(op)<-c("est0","lb0","ub0","est","lb","ub","i2","i2lb","i2ub","n","arms","tot", "cured","relapse")
rownames(op)<-NULL


op <- sapply(op,as.numeric)
op <- sapply(op, function(x) round(x,4))

op<-as.data.frame(t(op))
op$name<-catname

return(op)
}

```

1) Overall proportion of relapse: Overall
```{r echo=FALSE, message=FALSE, warning=FALSE}

library(readr)
library(readxl)
# meta-analysis packages
library(meta)
library(metafor)
#library(metagen)
library(metasens) 
# graphics packages
library(tidyverse)
library(reshape)
library(doBy)
library(stringr)
library(ggpubr)
library(patchwork)
library(dplyr)
library(data.table)


setwd("C:/Users/Rutuja Chhajed/OneDrive - Nexus365/IDDO/Analysis/VL_Analysis")
df_all<-readRDS('vl_final.RDS')



#Making sure, frel (Total relapses)= NA and nor 0, if values are not reported. What about the ones reporting only total?
df_all$frel<-ifelse(is.na(df_all$frel180)&is.na(df_all$frel360),NA,df_all$frel)
length(unique(df_all$pub_id))
#120 studies finally in our analysis!

#1. Overall estimate at 6 months and overall 
catname<-"Overall"
m<- metaprop(  data = df_all,  event =frel,  n=n_icured,   sm = "PLOGIT",  prediction=TRUE)
summary(m)

metabias(m,method.bias = "Egger")
#p<0.001
m_adj<-copas(m, gamma0.range=c(-3,5), gamma1.range=c(-1,2))
m_adj
o1<-m_extract(m_adj,catname)
rm(m,m_adj)

catname<-"Overall-6m"
m<- metaprop(  data = df_all,  event =frel180,  n=n_icured,   sm = "PLOGIT",  prediction=TRUE)
summary(m)

metabias(m,method.bias = "Egger")
#p<0.001

m_adj<-copas(m, gamma0.range=c(-2,5), gamma1.range=c(-1,2))
m_adj
o2<-m_extract(m_adj,catname)


m_table<-rbind(o1,o2)
rm(o1,o2)
```

2) By region
```{r}
#1.2: By region at 6 months
region<-unique(df_all$st_region)
b_pval<-NULL
#Carrying meta analysis for all regions and storing them in mr1, mr2...
for (i in 1:6){
  df_tmp<-subset(df_all,df_all$st_region==region[i])
               m_tmp<- metaprop(data = df_tmp,  event =frel180,  n=n_icured,   sm = "PLOGIT",  prediction=TRUE)
               assign(paste0("m_reg",i),m_tmp)}


m_adj<-copas(m_reg1, gamma0.range=c(-2,5), gamma1.range=c(0,2))
catname=m_adj$x$data$st_region[1]
or1<-m_extract(m_adj,catname)
metabias(m_reg1,method.bias = "Egger")
#p-value = 0.0002

m_adj<-copas(m_reg2, gamma0.range=c(-2,5), gamma1.range=c(0,2))
catname=m_adj$x$data$st_region[1]
or2<-m_extract(m_adj,catname)
metabias(m_reg2,method.bias = "Egger")
#(k=6) too small to test for small study effects 


#m_adj<-copas(m_reg3, gamma0.range=c(-2,5), gamma1.range=c(0,2))
catname=m_adj$x$data$st_region[1]
or3<-m_extract(m_adj,catname)
metabias(m_reg3,method.bias = "Egger")
# p-value = 0.1132

m_adj<-copas(m_reg4, gamma0.range=c(-2,5), gamma1.range=c(0,2))
catname=m_adj$x$data$st_region[1]
or4<-m_extract(m_adj,catname)
metabias(m_reg4,method.bias = "Egger")
# (k=8) too small to test for small study effects


m_adj<-copas(m_reg5, gamma0.range=c(-2,5), gamma1.range=c(0,2))
catname=m_adj$x$data$st_region[1]
or5<-m_extract(m_adj,catname)
metabias(m_reg5,method.bias = "Egger")
# (k=8) too small to test for small study effects


m_adj<-copas(m_reg6, gamma0.range=c(-2,5), gamma1.range=c(0,2))
catname=m_adj$x$data$st_region[1]
or6<-m_extract(m_adj,catname)
metabias(m_reg6,method.bias = "Egger")
# (k=7) too small to test for small study effects

m_table<-rbind(m_table, or1, or2,or3, or4, or5, or6)
b_pval_reg<-b_pval
rm(or1,or2,or3, or4, or5, or6)
rm(m_reg1, m_reg2, m_reg3, m_reg4, m_reg5, m_reg6)
rm(m_adj, m)


```



3) By drug regimen
```{r}
#1.3: By drug
drug<-unique(df_all$drugcat)
#Carrying meta analysis for all regions nad storing them in mr1, mr2...
for (i in 1:17){
  d=drug[i]
  df_tmp<-subset(df_all, df_all$drugcat== d)
               m_tmp<- metaprop(data = df_tmp,  event =frel180,  n=n_icured,   sm = "PLOGIT",  prediction=TRUE)
               assign(paste0("m_drug",i),m_tmp)}


m_adj<-copas(m_drug1, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
catname=m_adj$x$data$drugcat[1]
od1<-m_extract(m_adj,catname)
metabias(m_drug1,method.bias = "Egger")
# k small


m_adj<-copas(m_drug2, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
catname=m_adj$x$data$drugcat[1]
od2<-m_extract(m_adj,catname)
rm(m_adj)
metabias(m_drug2,method.bias = "Egger")
# p-value = 0.0815


m_adj<-copas(m_drug3, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
catname=m_adj$x$data$drugcat[1]
od3<-m_extract(m_adj,catname)
rm(m_adj)
metabias(m_drug3,method.bias = "Egger")
# p-value = 0.8776



m_adj<-copas(m_drug4, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
catname=m_adj$x$data$drugcat[1]
od4<-m_extract(m_adj,catname)
rm(m_adj)
metabias(m_drug4,method.bias = "Egger")
# p-value = k=9 too small


#m_adj<-copas(m_drug5, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_unadj<-m_drug5
catname=m_unadj$data$drugcat[1]
od5<-m_extract0(m_unadj,catname)


rm(m_unadj)
metabias(m_drug5,method.bias = "Egger")
# p-value = k small




m_adj<-copas(m_drug6, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
catname=m_adj$x$data$drugcat[1]
od6<-m_extract(m_adj,catname)
rm(m_adj)
metabias(m_drug6,method.bias = "Egger")
# p-value = 0.0053



m_adj<-copas(m_drug7, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
catname=m_adj$x$data$drugcat[1]
od7<-m_extract(m_adj,catname)
rm(m_adj)
metabias(m_drug7,method.bias = "Egger")
# p-value = k small



m_adj<-copas(m_drug8, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
catname=m_adj$x$data$drugcat[1]
od8<-m_extract(m_adj,catname)
rm(m_adj)
metabias(m_drug8,method.bias = "Egger")
# p-value = 0.229


m_adj<-copas(m_drug9, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
catname=m_adj$x$data$drugcat[1]
od9<-m_extract(m_adj,catname)
rm(m_adj)
metabias(m_drug9,method.bias = "Egger")
# p-value = 0.0028


m_adj<-copas(m_drug10, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
catname=m_adj$x$data$drugcat[1]
od10<-m_extract(m_adj,catname)
rm(m_adj)
metabias(m_drug10,method.bias = "Egger")
# p-value =  0.7672



m_adj<-copas(m_drug11, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
catname=m_adj$x$data$drugcat[1]
od11<-m_extract(m_adj,catname)
rm(m_adj)
metabias(m_drug11,method.bias = "Egger")
# p-value =  k small


m_adj<-copas(m_drug12, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
catname=m_adj$x$data$drugcat[1]
od12<-m_extract(m_adj,catname)
rm(m_adj)
metabias(m_drug12,method.bias = "Egger")
# p-value =  k small

m_adj<-copas(m_drug13, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
catname=m_adj$x$data$drugcat[1]
od13<-m_extract(m_adj,catname)
rm(m_adj)
metabias(m_drug13,method.bias = "Egger")
# p-value =  0.34


m_adj<-copas(m_drug14, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
catname=m_adj$x$data$drugcat[1]
od14<-m_extract(m_adj,catname)
rm(m_adj)
metabias(m_drug14,method.bias = "Egger")
# p-value = k small

m_adj<-copas(m_drug15, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
catname=m_adj$x$data$drugcat[1]
od15<-m_extract(m_adj,catname)
rm(m_adj)
metabias(m_drug15,method.bias = "Egger")
# p-value =  0.94

#m_adj<-copas(m_drug5, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_unadj<-m_drug17
catname=m_unadj$data$drugcat[1]
od17<-m_extract0(m_unadj,catname)


rm(m_unadj)
metabias(m_drug17,method.bias = "Egger")
# p-value = k small

m_table<-rbind(m_table, od1, od2, od3, od4,  od6, od7, od8, od9, od10, od11, od12, od13, od14, od15, od17)
rm(m_drug1, m_drug2, m_drug3, m_drug4, m_drug5, m_drug6, m_drug7, m_drug8, m_drug9, m_drug10, m_drug11, m_drug12, m_drug13, m_drug14, m_drug16,m_drug17, m_drug15, m_drug16,  m_drug17)

rm(od1, od2, od3, od4, od5, od6, od7, od8, od9, od10, od11, od12, od13, od14, od15, od17)
#Drug 16& 17: No. of studies too low
```

4) Relapse diagnosis method

```{r}
#1.3: Relapse Diagnosis Method

relapsediagmethod<-unique(df_all$rel_diag)
#Carrying meta analysis for all regions and storing them in mr1, mr2...
for (i in 1:4){
   rel<-relapsediagmethod[i]
   df_tmp<-subset(df_all,df_all$rel_diag==rel)
               m_tmp<- metaprop(data = df_tmp,  event =frel180,  n=n_icured,   sm = "PLOGIT",  prediction=TRUE)
               assign(paste0("m_rel",i),m_tmp)
               rm(m_tmp)}



m_adj<-copas(m_rel1, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
catname=m_adj$x$data$rel_diag[1]
orel1<-m_extract(m_adj,catname)
rm(m_adj)
metabias(m_rel1,method.bias = "Egger")
# p-value < 0.0001


m_adj<-copas(m_rel2, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
catname=m_adj$x$data$rel_diag[1]
orel2<-m_extract(m_adj,catname)
rm(m_adj)
metabias(m_rel2,method.bias = "Egger")
# p-value =0.148


m_adj<-copas(m_rel3, gamma0.range=c(-2,5), gamma1.range=c(-3,3))
m_adj
catname=m_adj$x$data$rel_diag[1]
orel3<-m_extract(m_adj,catname)
rm(m_adj)
metabias(m_rel3,method.bias = "Egger")
# p-value k small

#Value changes a lot with gamma0! ( 4 to 5)

m_adj<-copas(m_rel4, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
catname=m_adj$x$data$rel_diag[1]
orel4<-m_extract(m_adj,catname)
rm(m_adj)
metabias(m_rel4,method.bias = "Egger")
# p-value k small

m_table<-rbind(m_table, orel1, orel2, orel3, orel4)
rm(m_rel1, m_rel2, m_rel3, m_rel4)
rm(orel1, orel2, orel3, orel4)
```


4) Case mix

```{r}
casemix<-unique(df_all$cases_grouped)

for (i in 1:4){
  cm<-casemix[i]
   df_tmp<-subset(df_all,df_all$cases_grouped==cm)
               m_tmp<- metaprop(data = df_tmp,  event =frel180,  n=n_icured,   sm = "PLOGIT",  prediction=TRUE)
               assign(paste0("m_case",i),m_tmp)
               rm(m_tmp)}



m_adj<-copas(m_case1, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
catname=m_adj$x$data$cases_grouped[1]
ocase1<-m_extract(m_adj,catname)
rm(m_adj)
metabias(m_case1,method.bias = "Egger")
# p-value = 0.0004



m_adj<-copas(m_case2, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
catname=m_adj$x$data$cases_grouped[1]
ocase2<-m_extract(m_adj,catname)
rm(m_adj)
metabias(m_case2,method.bias = "Egger")
# p-value = 0.09


m_adj<-copas(m_case3, gamma0.range=c(-2,5), gamma1.range=c(-3,3))
m_adj
catname=m_adj$x$data$cases_grouped[1]
ocase3<-m_extract(m_adj,catname)
rm(m_adj)
metabias(m_case3,method.bias = "Egger")
# p-value = 0.0001

#Value changes a lot with gamma0! ( 4 to 5)

m_adj<-copas(m_case4, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
catname=m_adj$x$data$cases_grouped[1]
ocase4<-m_extract(m_adj,catname)
rm(m_adj)
metabias(m_case4,method.bias = "Egger")
# p-value = 0.9546


m_table<-rbind(m_table, ocase1, ocase2, ocase3, ocase4)
rm(m_case1, m_case2, m_case3, m_case4)
rm(ocase1, ocase2, ocase3, ocase4)



#Exploring unresponsive VL cases:

df1<-subset(df_all, df_all$cases_grouped=="Unresponsive VL")
```


```{r}
cols.num <- colnames(m_table[,1:9])
m_table[, cols.num] <- lapply(m_table[, cols.num, drop = FALSE],
                             function(x) x * 100)

write.csv(m_table,"Result_1.csv")
```


II. Stratified analysis by Region and Drug categories: For all studies at 6 month follow-up!

```{r echo=TRUE, message=FALSE, warning=FALSE}
#MAIN DATA SET FOR NOW!!
df_6m<-subset(df_all,df_all$rmt180>0)
df_6m<-subset(df_6m,df_6m$n_icured>0)
df_6m<-subset(df_6m,!df_6m$st_region=="Multi-Regional")

final<-NULL

drugcatlist<- c("LamB SD Mono" ,"LamB SD Comb",  "LamB MD Mono", "LamB MD Comb", "LamB UD Mono" ,"AmphB deoxycholate" ,"AmphB (FLCC)" ,"Miltefosine","Paromomycin" ,"Miltefosine & Paromomycin" ,"PA" ,"PA & Paromomycin"  ,"PA comb")    


for (i in 1:18){
  
tmp<- df_6m[which(df_6m$drugcat==drugcatlist[i]),]

if(nrow(tmp)==0) next
tmp<- droplevels(tmp)

m<- metaprop(
  data = tmp,
  event = frel180,#Relapse variable to be considered: Here it is at 180 days
  n=n_icured, 
  sm = "PLOGIT",
  prediction=TRUE
)
assign(paste0("m_",i),m)


#--------------------------------
# Subgroup analysis by Drug category
#--------------------------------
m_region<-update.meta(m, 
            byvar=st_region, 
            comb.random = TRUE, 
            comb.fixed = F)
assign(paste0("m_region_",i),m_region)



s<-summary(m_region)
s1<-s$within.random

est<- exp(s1$TE)/(1+exp(s1$TE))
est<-round(est,4)
lb<-exp(s1$lower )/(1+exp(s1$lower))
lb<-round(lb,3)
ub<-exp(s1$upper )/(1+exp(s1$upper))
ub<-round(ub,3)

i2<-s$I2.w
i2_est<- i2$TE
i2_lb<-i2$lower
i2_ub<-i2$upper
i2_est<-round(i2_est,3)
i2_lb<-round(i2_lb,3)
i2_ub<-round(i2_ub,3)

a<-NULL
a=s$within.predict$lower
p_lb<-exp(a)/(1+exp(a))

a<-NULL
a=s$within.predict$upper
p_ub<-exp(a)/(1+exp(a))

n<-s$k.w
region<-s$bylevs
dm<-cbind(region,n,est,lb,ub,i2_est,i2_lb,i2_ub,p_lb,p_ub)
dm<-as.data.frame(dm)
dm$drugcat<-drugcatlist[i]
dm<-dm[,c(11,1:10)]

o<-s$random
o_n<-s$k
o_est<-exp(o$TE)/(1+exp(o$TE))
o_lb<-exp(o$lower)/(1+exp(o$lower))
o_ub<-exp(o$upper)/(1+exp(o$upper))


oi2<-s$I2
a<-NULL
a=s$predict$lower
o_plb<-exp(a)/(1+exp(a))
a<-NULL
a=s$predict$upper
o_pub<-exp(a)/(1+exp(a))


o_row<-round(c(o_est,o_lb,o_ub,oi2$TE,oi2$lower,oi2$upper,o_plb,o_pub),3)
o_row<-c(drugcatlist[i],"Overall",o_n, o_row)


dm<-rbind(o_row,dm)


events_region<-tmp %>% 
  dplyr::group_by(st_region) %>%
  dplyr::summarise(
    n_studies 	= length(unique(pub_id)),
    n_event	= sum(frel180, na.rm = TRUE ), #Relapse variable to be considered: Here it is at 180 days
    n_cured	= sum(n_icured, na.rm = TRUE),
    n_totfu= sum(sa_num_tx, na.rm = TRUE))
colnames(events_region)[1]<-"region"


dm<-left_join(dm,events_region,by='region')

final<-rbind(final,dm)
assign(paste0("dm_",i),dm)
 
print(drugcatlist[i])
print(s)
}

final_store_rel<-final

setwd("C:/Users/Rutuja Chhajed/OneDrive - Nexus365/IDDO/Data")
drugcat_names <-read_excel("C:/Users/Rutuja Chhajed/OneDrive - Nexus365/IDDO/Data/DrugCategories.xlsx", 
    sheet = "drug cat full names")

final<-left_join(final,drugcat_names,by="drugcat")

final<-final[,c("Drug Category", "region",  "n_studies","n","n_totfu","n_cured","n_event","est", "lb","ub","i2_est","i2_lb","i2_ub","p_lb","p_ub")]

colnames(final)<-c("Drug Category","Region","Studies","Arms","Tot FU","In. cured", "Relapses", "Est","lb","ub","I2","i2_lb","i2_ub","p_lb","p_ub")


cols.num <- c( "Est","lb","ub","I2","i2_lb","i2_ub","p_lb","p_ub")
final[cols.num] <- sapply(final[cols.num],as.numeric)
final[, cols.num] <- lapply(final[, cols.num, drop = FALSE],
                             function(x) x * 100)

final[, cols.num] <- lapply(final[, cols.num, drop = FALSE],
                             function(x) round(x,2))

setwd("C:/Users/Rutuja Chhajed/OneDrive - Nexus365/IDDO/Data/Results")
write.csv(final,"MA_drugcat_region_6m_0301.csv")#Change date and name
#Do prop.test for i=4 and 7 (Med)
#Manually updated results in Excel
```
Plotting Drug-Region sub group analysis

```{r}
library(readxl)
res_6m <- final

colnames(res_6m)<-c("drug_category", "region",  "n_studies","arms","n_totfu","n_cured","n_event","est", "lb","ub","i2_est","i2_lb","i2_ub","p_lb","p_ub")
res_6m$id<-paste0(res_6m$drug_category,res_6m$region)

# Make every country unique
res_6m$region<-factor(res_6m$region,levels = c(  "Mediterranean","Central Asia" , "South America","Eastern Africa","India Subcontinent","Overall"   ))

r<-subset(res_6m,res_6m$drug_category%in% c("LAmB (Single dose) Mono regimen"   , "LamB (Single dose) Combination regimen"  ,"LamB (Multiple dose) Mono regimen" ))
r$region<-factor(r$region,levels = c( "Mediterranean","Central Asia" , "South America","Eastern Africa","India Subcontinent","Overall"   ))


library(RColorBrewer)

#define custom color scale
myColors <- brewer.pal(6, "Dark2")
names(myColors) <- levels(r$region)
myColors[6]<-"#E7298A"
myColors[4]<- "#1E3F66"
custom_colors <- scale_colour_manual(values = myColors)

p <- ggplot(r, aes(x=region, y=est, ymin=lb, ymax=ub,colour = region)) + geom_pointrange( size=1.05,aes(colour = region))+
#+ coord_cartesian(ylim=c(0, 30))+
  coord_flip()+ ylab("Relapse Proportion at 6month (%)")+xlab("")+labs("Region")+
  facet_wrap(~ drug_category, ncol = 1) +  theme(panel.background = element_rect(fill = "white"),panel.grid.major = element_line("lightgray",0.5),
        panel.grid.minor = element_line("lightgray",0.25))+ custom_colors




r1<-subset(res_6m,res_6m$drug_category%in% c("Amphotericin B deoxycholate"  , "Amphotericin b (fat/lipid/colloid/cholestrol)"))

p1 <- ggplot(r1, aes(x=region, y=est, ymin=lb, ymax=ub,colour = region)) + geom_pointrange( size=1.05,aes(colour = region))+
#+ coord_cartesian(ylim=c(0, 30))+
  coord_flip()+ ylab("Relapse Proportion at 6month (%)")+xlab("")+labs("Region")+
  facet_wrap(~ drug_category, ncol = 1) +  theme(panel.background = element_rect(fill = "white"),panel.grid.major = element_line("lightgray",0.5),
        panel.grid.minor = element_line("lightgray",0.25))+ custom_colors
p1


r2<-subset(res_6m,res_6m$drug_category %in% c("Miltefosine"  ,"Paromomycin","Miltefosine & Paromomycin"  ,"Pentavalent antimonial" , "Pentavalent antimonial & Paromomycin"))

p2 <- ggplot(r2, aes(x=region, y=est, ymin=lb, ymax=ub,colour = region)) + geom_pointrange( size=1.05,aes(colour = region))+
#+ coord_cartesian(ylim=c(0, 30))+
  coord_flip()+ ylab("Relapse Proportion at 6month (%)")+xlab("")+labs("Region")+
  facet_wrap(~ drug_category, ncol = 1) +  theme(panel.background = element_rect(fill = "white"),panel.grid.major = element_line("lightgray",0.5),
        panel.grid.minor = element_line("lightgray",0.25))+ custom_colors
p2


```


III) 6 month vs 12 month
Focus on 13 studies with follow up duration of more than 6 months

```{r}
df_612<-subset(df_all,(df_all$rmt360==1&df_all$rmt180>0))
length(unique(df_612$pub_id))
#19 studies with relapses at 6 and 12 months!
#Sum of relapses at 6 and >6 months. If one is NA--> treated as 0
#Useless measure

#For 12 months follow up studies, not <12 but at 12 months!!
#Relapse_time is a confusing variable: Puts noted relapse cases, it is NOT FOLLOW UP DURATION!!!
#eff_relapse_days is not correctly written either.

#For now, all studies with rmt360==1 and relapse_time =! 240,270

#df_5<-subset(df_5,!df_5$relapse_time%in% c("240","270"))


ro<- metaprop(
  data =df_612,
  event =  frel,
  n=n_icured, 
  sm = "PLOGIT",
  prediction=TRUE)

r12<- metaprop(
  data =df_612,
  event =  frel360,
  n=n_icured, 
  sm = "PLOGIT",
  prediction=TRUE)

r6<- metaprop(
  data =df_612,
  event =  frel180,
  n=n_icured, 
  sm = "PLOGIT",
  prediction=TRUE)


m_adj<-copas(ro, gamma0.range=c(-2,5), gamma1.range=c(0,2))
metabias(ro,method.bias = "Egger")
catname<-"spec-overall"
o1<-m_extract(m_adj,catname)


m_adj<-copas(r6, gamma0.range=c(-3,6), gamma1.range=c(-1,3))
m_adj
metabias(r6,method.bias = "Egger")
catname<-"Spec-6m"
o2<-m_extract(m_adj,catname)

m_adj<-copas(r12, gamma0.range=c(-2,5), gamma1.range=c(0,2))
metabias(r12,method.bias = "Egger")
catname<-"Spec-12m"
o3<-m_extract(m_adj,catname)

results_6vs12<-rbind(o1,o2,o3)

events1<-df_612 %>% 
  dplyr::summarise(
    n_studies 	= length(unique(pub_id)),
    n_event	= sum(frel180, na.rm = TRUE), #Relapse variable to be considered: Here it is at 180 days
    n_cured	= sum(n_icured),
    n_totfu= sum(sa_num_tx))

events2<-df_612 %>% 
  dplyr::summarise(
    n_studies 	= length(unique(pub_id)),
    n_event	= sum(frel), #Relapse variable to be considered: Here it is at 180 days
    n_cured	= sum(n_icured),
    n_totfu= sum(sa_num_tx))

events3<-df_612 %>% 
  dplyr::summarise(
    n_studies 	= length(unique(pub_id)),
    n_event	= sum(frel360), #Relapse variable to be considered: Here it is at 180 days
    n_cured	= sum(n_icured),
    n_totfu= sum(sa_num_tx))

n_event<-c(events2[1,2], events1[1,2],events3[1,2])
results_6vs12$relapse<-n_event


results_6vs12[, 1:9] <- lapply(results_6vs12[, 1:9, drop = FALSE],
                             function(x) x * 100)


write.csv(results_6vs12,'Results2.csv')
```


For Indian Subcontinent, LamB SD: Dosage and relapse relationship

```{r}
df_ind<-subset(df_all,df_all$st_region=="India Subcontinent")
df_ind$sa_int1_total_dose<-as.numeric(df_ind$sa_int1_total_dose)

df_ind1<-subset(df_ind,df_ind$drugcat=="LamB SD Mono")
df_ind1<-subset(df_ind1,df_ind1$frel180>=0)

df_ind1$sa_int1_total_dose<-as.numeric(df_ind1$sa_int1_total_dose)
df_ind1$total_dose<-ifelse(df_ind1$sa_int1_total_dose<=5,1,ifelse(df_ind1$sa_int1_total_dose<=10,2,3))
table(df_ind1$sa_int1_total_dose)
table(df_ind1$total_dose)

for (i in 1:3){
   df_tmp<-subset(df_ind1,df_ind1$total_dose==i)
               m_tmp<- metaprop(data = df_tmp,  event =frel180,  n=n_icured,   sm = "PLOGIT",  prediction=TRUE)
               assign(paste0("m_dose",i),m_tmp)
               rm(m_tmp)}


#Do it manually: FILL IN THE UNADJUSTED VALUES
m_adj<-copas(m_dose1, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
catname=m_adj$x$data$total_dose[1]
odose1<-m_extract(m_adj,catname)
rm(m_adj)
metabias(m_dose1,method.bias = "Egger")
# Just 1 study; No bias etc

m_adj<-copas(m_dose2, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
catname=m_adj$x$data$total_dose[1]
odose2<-m_extract(m_adj,catname)
rm(m_adj)
metabias(m_dose2,method.bias = "Egger")
# No. of study too small to study small study effect
#Adjusted estimate very similar to unadj


m_adj<-copas(m_dose3, gamma0.range=c(-2,5), gamma1.range=c(0,2))
m_adj
catname=m_adj$x$data$total_dose[1]
odose3<-m_extract(m_adj,catname)
rm(m_adj)
metabias(m_dose3,method.bias = "Egger")
# No. of study too small to study small study effect
#Adjusted estimate very similar to unadj

m_dose<-rbind(odose2,odose3)
#Performs chi-squared test for trend in proportion. This test is also known as Cochran-Armitage trend test.
#Wrappers around the R base function prop.trend.test() but returns a data frame for easy data visualization.


df_ind1$n_defcure<-df_ind1$n_icured-df_ind1$frel180
df_ind1$notf<-df_ind1$sa_num_tx-df_ind1$compo

xtab<-as.table(cbind(df_ind1$frel180,df_ind1$n_defcure))
xtab1<-as.table(cbind(df_ind1$compo,df_ind1$notf))

library('rstatix')
prop_trend_test(xtab,df_ind1$total_dose)
#P=0.13

prop_trend_test(xtab1,df_ind1$total_dose)
#P=0.05



m_dose[, 1:9] <- lapply(m_dose[, 1:9, drop = FALSE],
                             function(x) x * 100)


write.csv(m_dose,'Results3.csv')
```

```{r}
library('lme4')
model1<- glmer(cbind(frel180,n_defcure) ~   sa_int1_total_dose + (1 | id) ,
              family = binomial, data = df_ind1)

summary(model1)


model1a<- glmer(cbind(frel180,n_defcure) ~   sa_int1_total_dose +rel_diag+(1 | id) ,
              family = binomial, data = df_ind1)

summary(model1a)


model2<- glmer(cbind(compo,notf) ~   sa_int1_total_dose + (1 | id) ,
              family = binomial, data = df_ind1)

summary(model2)
```

Time trend analysis:

```{r}
setwd("C:/Users/Rutuja Chhajed/OneDrive - Nexus365/IDDO/Data")
vl_main <-read_csv("VL_cleandata_0222.csv")
df_all$key<-paste0(df_all$pub_id,"_",df_all$redcap_repeat_instance)
df<-left_join(df_all,vl_main[,c('key','pub_year')])
df$pub_year<-as.numeric(df$pub_year)

df$decade<-ifelse(df$pub_year<1990,"80s",ifelse(df$pub_year<2000,"90s",ifelse(df$pub_year<2010,"00s","10s")))

m<- metaprop(
  data = df,
  event = frel180,#Relapse variable to be considered: Here it is at 180 days
  n=n_icured, 
  sm = "PLOGIT",
  prediction=TRUE
)


m_decade<-update.meta(m, 
            byvar=decade, 
            comb.random = TRUE, 
            comb.fixed = F)

```

